Formatting instructions for NIPS 2018

### 2018-05-08 NIPS 2018/main.tex

When learning the optimal value function, a quantity of interest is how close a given $Q$-function is to the fixed-point of the Bellman operator. This is given by its Bellman residual, defined by $B(Q) \triangleq TQ - Q$. Notice that $Q$ is optimal if, and only if, $B(Q)(s,a) = 0$ for all $s,a$. Furthermore, if we assume the existence of a distribution $\mu$ over $\mathcal{S}\times\mathcal{A}$, the expected squared Bellman error of $Q$ is defined as the expected squared Bellman residual of $Q$ under $\mu$, $\mathbb{E}_{\mu}\left[ B^2(Q) \right]$. Although minimizing the empirical Bellman error is an appealing objective, it is well-known that an unbiased estimator requires two independent samples of the next state $s'$ of each $s,a$ (e.g., \cite{} \todo{cite Maillard}). In practice, the empirical Bellman error is typically replaced by the TD error, which approximates the former using a single transition sample. Given a dataset of $N$ samples, the TD error is computed as $\frac{1}{N}\sum_{i=1}^N (r_i + \gamma \max_{a'} Q(s_i',a') - Q(s_i,a_i))^2$.

>>>>

When learning the optimal value function, a quantity of interest is how close a given $Q$-function is to the fixed-point of the Bellman operator. This is given by its Bellman residual, defined by $B(Q) \triangleq TQ - Q$. Notice that $Q$ is optimal if, and only if, $B(Q)(s,a) = 0$ for all $s,a$. Furthermore, if we assume the existence of a distribution $\nu$ over $\mathcal{S}\times\mathcal{A}$, the squared Bellman error of $Q$ is defined as the expected squared Bellman residual of $Q$ under $\nu$, $\norm{B(Q)}_{\nu}^2=\mathbb{E}_{\mu}\left[ B^2(Q) \right]$. Although minimizing the empirical Bellman error is an appealing objective, it is well-known that an unbiased estimator requires two independent samples of the next state $s'$ of each $s,a$ (e.g., \cite{} \todo{cite Maillard}). In practice, the empirical Bellman error is typically replaced by the TD error, which approximates the former using a single transition sample. Given a dataset of $N$ samples, the TD error is computed as $\norm{B(Q)}_{D}^2 = \frac{1}{N}\sum_{i=1}^N (r_i + \gamma \max_{a'} Q(s_i',a') - Q(s_i,a_i))^2$.
